Auditory Scene Similarity Retrieval and Classification with Relevance-based Quantization of Scattering Features

### 2017-05-01 paper/structureScene.tex
addition of reference pdfs
fix small mistake in section IV intro
typo

\documentclass[journal]{IEEEtran}
%\usepackage{cite}
% *** GRAPHICS RELATED PACKAGES ***
%
\ifCLASSINFOpdf
  \usepackage[pdftex]{graphicx}
\fi
%
\usepackage[cmex10]{amsmath}

@@

\usepackage[backend=bibtex,style=numeric-comp,sorting=none,firstinits=true]{biblatex}
\bibliography{biblio}
%\renewcommand{\baselinestretch}{2}

@@

Prior to constructing models (for classification or similarity estimation), it is beneficial to process scattering coefficients to improve invariance, normality, and generalization power.
In this section, we review three transformations which achieve these properties, namely logarithmic compression and standardization.

@@

/ support vector machine (SVM) is a binary discriminative classifier that attempts to find a separating hyperplane between a pair of classes of that provides the maximal margin between the two sets \cite{Cortes1995}. From another point of view, it attempts to find a direction on which to project in order to maximize separation between two point clouds. Since it is not a generative, but discriminative model, it is able to pick out those feature vectors that best characterize a particular class of auditory scenes compared to another. This property, coupled with its ease of use and efficient implementations \cite{libsvm} have rendered SVMs a popular choice for many classification systems.

>>>>

\documentclass[onecolumn,journal]{IEEEtran}
%\usepackage{cite}
% *** GRAPHICS RELATED PACKAGES ***
%
\ifCLASSINFOpdf
  \usepackage[pdftex]{graphicx}
\fi
%
\usepackage[cmex10]{amsmath}

@@

\usepackage[backend=bibtex,style=numeric-comp,sorting=none,firstinits=true]{biblatex}
\bibliography{biblio}
\renewcommand{\baselinestretch}{2}

@@

Prior to constructing models (for classification or similarity estimation), it is beneficial to process scattering coefficients to improve invariance, normality, and generalization power.
In this section, we review two transformations which achieve these properties, namely logarithmic compression and standardization.

@@

A support vector machine (SVM) is a binary discriminative classifier that attempts to find a separating hyperplane between a pair of classes of that provides the maximal margin between the two sets \cite{Cortes1995}. From another point of view, it attempts to find a direction on which to project in order to maximize separation between two point clouds. Since it is not a generative, but discriminative model, it is able to pick out those feature vectors that best characterize a particular class of auditory scenes compared to another. This property, coupled with its ease of use and efficient implementations \cite{libsvm} have rendered SVMs a popular choice for many classification systems.
